---
title: "Data Report"
author: "RuoluYe"
date: "5/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("analysis.R")
```

## Summary Information
This report is about mass shootings in 2018. The data is retrieved from<http://www.shootingtracker.com/>, a total of `r shooting_occurred` shootings have occured in 2018, with a total of `r live_lost` people have been killed. 
The city that was most impacted by mass shootings (based on the total number of deaths and injuries in the cities) is `r city_most_impact`. 
The state that was most impacted is `r state_most_impact`.
The date in 2018 that has most peopele killed or injured due to mass shootings is/are `r miserable_day`.

## Summary Table
This summary table lists the total number of victims(killed and injured) in each city due to mass shootings in 2018. 
The cities are sorted from the highest number of victims to the lowest. 
```{r data, echo=FALSE, comment=""}
print.data.frame(summary_table)
```
From this table, we can tell that the Chicago is the city with most victims. It is far more impacted by mass shottings than any other cities in the U.S. becasue there were almost three times as many victims as the second place cities, and it is the only city that has the number of victims over 100 in 2018.

## Description of a Particular Incident
For the city Baltimore, Maryland, the incident with most victims in 2018 happened on `r date` at `r address`. There were `r victim` people who were hurt in this incident. There were `r killed` deaths and `r injured` injuries. According to [_The Baltimore Sun_](https://www.baltimoresun.com/news/crime/bs-md-ci-shootings-20180701-story.html), "The victims’ injuries were not life-threatening, police said. Detectives and officers are canvassing the neighborhood and interviewing witnesses."

## Interactive Map
Here is an interactive map based on the data of mass shootings in 2018 in the U.S.
`r map`
From this map, we can tell that there were much more shootings happened on the East coast. 
In the southeast city Pompano Beach, there is a mass shooting that caused 17 deaths and 17 injuries, whic marks a large circle on the map. 

## Plot
Below is an interacive bar chart that shows the total number of victims due to mass shootings in each month in the year of 2018. 
`r interactive_chart`
My question is, in which month is there most victim due to mass shootings? 

The bar chart shows us that the month with most people killed and injuried under mass shootings is June. 
I chose to use a bar chart becasue bar chart is good at comparing numbers with the height of each bar. My question was asking the heighest number of victims, and the bar chart visualizes number into bars, with higher bar for larger number. In this way, I can easily tell that the bar for month June is heighest and can answer the question. 




